Contextual Combinatorial Cascading Bandits

### 2016-02-04 contextual combinatorial cascading bandits.tex
update

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion.
In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We further consider position discounts in the list order, which means the agent's reward is discounted depending on the position where the stopping criterion is met.
We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving context information and position discounts.

@@

The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; Section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; Section 5 demonstrates the experimental results; and section 6 gives a final conclusion.

@@

We first discuss several studies most relevant to our work.
Table \ref{table:outline} summarizes the different settings of these work, 
	which we will explain in details next.
A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
	after we provide the full result of our regret bound.

@@

The assumption of Lipschitz continuity gives an estimate of changes in reward function. To obtain a good estimation of reward function, the position $k$ with large $\gamma_k$ needs a good estimation of $w(a_k)$. This means the positions with large $\gamma_k$ are more important to the reward function. For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.

Notice that we do not require the knowledge how $f(A, w)$ is defined. We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$. In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve. For this reason, in the regret defined next, we compare our online algorithm with the best offline algorithm generates, $\alpha f_t^{\ast}$. More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$.

@@

Before presenting the algorithm, we explain the main ideas in the design.

By Eq.~\eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
To estimate the expected reward, we reduce to the estimation of $\theta_{\ast}$, which can be obtained by the ridge regression on $x$ and samples of $\bw$. In details, using the ridge regression on data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we obtain a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, restated as follows.

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	Note $w_{t,a} = \theta_*^{\top} x_{t,a}$. By H\"{o}lder's inequality,
	\begin{align*}
		&\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} = \abs{[\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})]^{\top} (\bV_{t-1}^{-1/2}x_{t,a})}\\
		\leq &~\norm{\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})}_2 \norm{\bV_{t-1}^{-1/2}x_{t,a}}_2\\
		=&~\norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		\leq&~ \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Because $1 - \theta_*^{\top} x_{t,a} \geq 0$ and
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	we can obtain the claimed result.
\end{proof}

@@

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

The more items reveals, the more reward the agent should receive. This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

@@

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$ with $f_t^{\ast} = \max_{A \in \cS} f(A, w_t)$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{\alpha f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) + \alpha \sqrt{n} \nonumber \\
		=&O\left(\frac{d}{\alpha f^{\ast}}\sqrt{nK} \ln(C_{\gamma} n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

\begin{figure*}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.9$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-9.eps}}
	\subfigure[Conjunctive, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-1.eps}}
	\subfigure[Conjunctive, $\gamma=0.9$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-9.eps}}
	\caption{Synthetic Data Set, L=100, K=4, d=10}
	\label{fig:synthetic} % 用于交叉引用
\end{figure*}

@@

We evaluated $C^3$-UCB in three experiments and compare our algorithm to {\it CombCascade}, the most related one to ours. And we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.

@@

\begin{figure}
	\centering
	\subfigure[$\gamma = 1$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
	\subfigure[$\gamma = 0.9$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
	\caption{MovieLens, L=200, K=4, d=5}
	\label{fig:movielens} % 用于交叉引用
\end{figure}

\begin{figure*}
	\centering
	\subfigure[Network 1239, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{isp1239-T5-k100-1.eps}}
	\subfigure[Network 3356, $\gamma = 0.9$]{
		\includegraphics[height = 3 cm, width = 4 cm]{isp3356-T5-k100-9.eps}}
	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{isp1755-T300000-gamma9-latency.eps}}
	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{network-gamma-with-point.eps}}
	\caption{Network, $d=10$}
	\label{fig:network} % 用于交叉引用
\end{figure*}

@@

For this experiment, we randomly chose $L=200$ movies and recommended $K=4$ movies at each time. We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}. The results for rewards are shown in Fig.~\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.

\subsection{Network Routing Data}

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for a general reward function and two special reward functions. The experiments conducted demonstrate the advantage to involve context information and position discounts. A matching lower bound on the regret bound is left for a future study.

>>>>

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion.
In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We further consider position discounts in the list order, which means the agent's reward is discounted depending on the position where the stopping criterion is met.
We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} with general reward functions and position discounts; Section 4 gives our algorithm and main results both on general reward functions and two special reward functions; Section 5 demonstrates the experimental results; and Section 6 gives a final conclusion.

@@

We first discuss several studies most relevant to our work.
Table \ref{table:outline} summarizes the different settings of these work, 
	which we will explain in details next.
A comparison of regret bounds by different methods is deferred to Section \ref{sec:diss},
	after we provide the full results of our regret bounds.

@@

The assumption of Lipschitz continuity gives an estimate of changes in the reward function. To obtain a good estimation of the reward function, the position $k$ with large $\gamma_k$ needs a good estimation of $w(a_k)$. This means the positions with large $\gamma_k$ are more important to the reward function. For example in website recommendations, the learning agent will receive the highest reward if the user selects the first item, so the first position is the most important.

Notice that we do not require the knowledge how $f(A, w)$ is defined. We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$. More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$. In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve. For this reason, in the regret defined next, we compare our online algorithm with the best offline algorithm generates, $\alpha f_t^{\ast}$.

@@

Before presenting the algorithm, we explain the main ideas in the design. By Eq.\eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
To estimate the expected reward, we reduce to the estimation of $\theta_{\ast}$, which can be obtained by the ridge regression on $x$ and samples of $\bw$. In details, using the ridge regression on data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is a column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we obtain a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, restated as follows.

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	Note $w_{t,a} = \theta_*^{\top} x_{t,a}$. By H\"{o}lder's inequality,
	\begin{align*}
		&\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} = \abs{[\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})]^{\top} (\bV_{t-1}^{-1/2}x_{t,a})}\\
		\leq &~\norm{\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})}_2 \norm{\bV_{t-1}^{-1/2}x_{t,a}}_2\\
		=&~\norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		\leq&~ \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Because $1 - \theta_*^{\top} x_{t,a} \geq 0$ and
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	the claimed result is obtained.
\end{proof}

@@

Now let us introduce a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{equation}
\label{eq:OrRewardFunc}
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). 
\end{equation}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

The more items reveals, the more reward the agent should receive. This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
	\end{cases}\\
	%&=\begin{cases}
	%	1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
	%	1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
	%\end{cases}
\end{align*}

@@

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$ with $f_t^{\ast} = \max_{A \in \cS} f(A, w_t)$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{\alpha f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) + \alpha \sqrt{n} \nonumber \\
		=&O\left(\frac{d}{\alpha f^{\ast}}\sqrt{nK} \ln(C_{\gamma} n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity. And then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

\begin{figure}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synD-T5-L100-K4-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.9$]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synD-T5-L100-K4-9.eps}}\\
	\subfigure[Conjunctive, $\gamma=1$ ]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synC-T5-L100-K4-1.eps}}
	\subfigure[Conjunctive, $\gamma=0.9$ ]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{synC-T5-L100-K4-9.eps}}
	\caption{Synthetic Data Set, L=100, K=4, d=10}
	\label{fig:synthetic} % 用于交叉引用
\end{figure}

@@

We evaluated $C^3$-UCB in three experiments and compared our algorithm to {\it CombCascade}, the most related one to ours. And we set the position discounts $\gamma_k$ to be $\gamma^{k-1}$ for some $\gamma$.

@@

\begin{figure}
	\centering
	\subfigure[$\gamma = 1$]{
		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
	\subfigure[$\gamma = 0.9$]{
		\includegraphics[height = 2.9cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
	\caption{MovieLens, L=200, K=4, d=5}
	\label{fig:movielens} % 用于交叉引用
\end{figure}

@@

For this experiment, we randomly chose $L=200$ movies and recommended $K=4$ movies at each time. We experimented with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compared our algorithm with {\it CombCascade}. The results for rewards are shown in Fig.\ref{fig:movielens} and demonstrate the advantage to involve context information in real applications.

\subsection{Network Routing Data}
\begin{figure}
	\centering
	\subfigure[Network 1239, $\gamma=1$]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp1239-T5-k100-1.eps}}
	\subfigure[Network 3356, $\gamma = 0.9$]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp3356-T5-k100-9.eps}}\\
	\subfigure[Rewards on network 1755 with latency, $\gamma = 0.9$ ]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{isp1755-T300000-gamma9-latency.eps}}
	\subfigure[Comparison of different $\gamma$ with true $\gamma^{\ast} = 0.9$, $n = 10000$ ]{
		\includegraphics[height = 2.9 cm, width = 3.95 cm]{network-gamma-with-point.eps}}
	\caption{Network, $d=10$}
	\label{fig:network} % 用于交叉引用
\end{figure}

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions. The experiments conducted demonstrate the advantage to involve context information and position discounts. A matching lower bound on the regret bound is left for a future study.
